A Constraint Solving Approach to Parikh Images of Regular Languages

### 2023-05-25 introduction.tex
More work on introduction

@@

  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[scale=\autscale]{a}
    \caption{The automaton $A'$, whose Parikh registers count both the number of letters and the start ($l$) and length ($r$) of the substring.}\label{fig:aut_a}
      %\Description[SHORT]{LONG}
  \end{subfigure}
\end{figure}s

>>>>

In this section we will introduce an intuition for how a string constraint problem in an automata-based solver like \OstrichPlus{} is translated to a Parikh automata intersection problem and solved efficiently using \Calculus{}. First, by a Parikh automaton we mean a standard Non-deterministic finite automaton (NFA) with a set of Parikh registers that are incremented (or decremented) at each transition. In the automata of \cref{fig:examples}, we will use the notation $a / \begin{bmatrix} x_+ \end{bmatrix}$ to mean that a transition reads an input character $a$ and increments register $x$ by one. We will omit any zero-valued increments and assume that all registers are scoped to their automaton.

Furthermore, we use $\CountOf{c}(A)$ to refer to the number of letters $c$ in $A$, and allow this expression to be used both in the input language of \cref{ex:string-constraints} and in the langauge of constraints that we translate to. Where $A$ is apparent, we will omit it.

@@

  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[scale=\autscale]{a}
    \caption{The automaton $A'$, whose Parikh registers count both the number of letters and the start ($l$) and length ($r$) of the substring.}\label{fig:aut_a}
      %\Description[SHORT]{LONG}
  \end{subfigure}
  \caption{The collection of automata we use as running examples}\label{fig:examples}
\end{figure}
